Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-01-25 docs/papers/roofline_model/gocean_roofline.tex
roofline: add more discussion of roofline results
roofline: add note to paper re next stage

In Figure~\ref{FIG_roofline_haswell} we plot the Roofline model
obtained for the E5-1620 CPU. In order to investigate the poor
performance of the u-Momentum kernel of NEMOLite2D, we also show the
performance of the (simpler) Continuity kernel from that code. As we
would expect, the performance of the u-Momentum kernel remains poor on
this CPU. However, the Continuity kernel performs well. The
working-set sizes for this kernel for the $128^2$ and $256^2$ domains
are approximately 1~MB and 4.2~MB, respectively. Both of these should
therefore fit comfortably in L3 cache. However, again, this kernel is
one of several within the time-stepping loop of NEMOLite2D. For the
$128^2$ domain this loop as a whole has a working-set size of
$18\times128^2\times 8$ bytes or 2.4~MB. {\bf Again, this should all
  fit comfortably in l3 cache so why are we nowhere near the L3
  bandwidth limit?}

>>>>

In Figure~\ref{FIG_roofline_haswell} we plot the Roofline model
obtained for the E5-1620 CPU. In order to investigate the poor
performance of the u-Momentum kernel of NEMOLite2D, we also show the
performance of the (simpler) Continuity kernel from that code. As we
would expect, the performance of the u-Momentum kernel remains poor on
this CPU. However, the Continuity kernel performs well. The
working-set sizes for this kernel for the $128^2$ and $256^2$ domains
are approximately 1~MB and 4.2~MB, respectively. Both of these should
therefore fit comfortably in L3 cache. However, again, this kernel is
one of several within the time-stepping loop of NEMOLite2D. For the
$128^2$ domain this loop as a whole has a working-set size of
$18\times128^2\times 8$ bytes or 2.4~MB. {\bf Again, this should all
  fit comfortably in l3 cache so why are we nowhere near the L3
  bandwidth limit? Need to look at performance variation with problem size and maybe HWPCs at the same time.}
